Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-23 cav2017/cav2017.tex
more revision of the AA based CEGIS sec

\begin{enumerate}
\item Calculate $\mat{T}$ as $\mat{W}_{cf}\mat{W}^{-1}$. %using equations \eqref{eq:rncf}\eqref{eq:rcf}\eqref{eq:to_cf}
\item Extract the Plant's characteristic polynomial coefficients from $P_a$. %the last row of $P_a=(\mat{T}\mat{A}\mat{T}^-1)_{n*}$.
\item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors: %($\frac{q_1}{2},\frac{q_2}{2},q_3$)
$$N=\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] 
\wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
\item Calculate a set of initial bounds on K based on the input constraints. $$\phi_{safety} \Leftrightarrow u_k=r-Kx_k : x \in X^\# \wedge u_k \in [\underline{u}\ \ \overline{u}]$$
\end{enumerate}
\item Next we synthesise a candidate controller. 
We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a single iteration, in addition to a stability specification defined by Jury's criteria. %, and try to synthesise a controller that meets these specs.
% For a stabilized closed-loop, which is necessary for our safety property, we need
% these roots to remain within the unit circle, which we verify using Jury's criteria.
% Notice that in our polynomials $c_0=1$ and we only use reals.
% Once we have established convergence, we may examine the 
% safety specification $\phi_{safety}$.

Let $\mathcal{J}\langle I,F \rangle (P,\mat{T})$ be a program describing Jury's method.
\begin{enumerate}
\item Select a controller $\tilde{\mat{K}} \in \mathbb{R}\langle I,F\rangle^n$. This is achieved by solving a SAT formula $\mathcal{J}_K=\mathcal{J}\langle I,F \rangle (P_{a-k},\mat{T})\wedge \phi_{input}$ that satisfies the input constraint and Jury's criteria for $P_{a-k}=z^n+\sum_{i=1}^n (a_i-k_i) z^{n-i} : k_i \in \mat{K} \wedge \mat{K}=\tilde{\mat{K}}\mat{T}$.
\item If there is no candidate solution we return UNSAT and exit the loop.
\end{enumerate}
\item Once we have a candidate solution, we perform a safety verification using abstract acceleration. For this purpose, we make use of a second abstraction that encompasses the accelerated continuous reach-tube over an unbounded time. % If this step fails, we find a counterexample iteration and initial state and create a new constraint to refine our abstraction.
%
The first step constraints
\begin{equation}
\mat{K} \models u_k=-\mat{K}x_k : \phi_{safety}
\label{eq:of_bounds}
\end{equation}
The second step is evaluating the progression of the system over time to evaluate 
$x_{k+1} \models \phi_{safety}$. For this step we require 
an initial set from which the system progresses. Obviously, this set $x_0$ 
must satisfy the specification; otherwise, the system will be unsafe to begin with.
We accept a specification in the form $\mat{E}\mat{T}x_0<\mat{f}$. 
The presence of $\mat{T}$ is because this will typically be given in the original 
state-space. Accelerating \eqref{eq:observer_LTI_cf}, we obtain:
%
\begin{align}
\label{eq:acc_observer_LTI_cf}
x=&\mat{A}_t^kx_0
%+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{t} r_i
+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{n}(\nu_1+\nu_2+\nu_3) : x_0 \models \phi_{init}
\end{align}
which would still require us to verify the system for every $k$ up to infinity. 
Instead we use abstract acceleration~\cite{cattaruzza2015unbounded}, which translates the formula into
%
\begin{align}
\label{eq:aa_observer_LTI_cf}
\hat{X}^\#
=&\mathcal{A}_t X_0+\mathcal{B}_{t} R + \mathcal{B}_{n} N\\
X_0 =&\left \{x : x \models \phi_{init} \right\}\nonumber\\
% R =&\{r : \mat{E}_r < f_r \}\nonumber\\
 %N=&\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] \wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber
\end{align}
%
where $\mathcal{A}_t=\bigcup_{k=1}^\infty \mat{A}^k, \mathcal{B}_{t}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{t}, \mathcal{B}_{n}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{n}$ are abstract matrices for the system in \eqref{eq:observer_LTI_cf} 
%and $r$ is a non-deterministic parametric input (\emph{ie} $\forall k>0, r_{k+1} =r_k$) 
whereas the set N is composed of non-deterministic variable inputs.

>>>>

\begin{enumerate}
\item Calculate $\mat{T}$ as $\mat{W}_{cf}\mat{W}^{-1}$. %using equations \eqref{eq:rncf}\eqref{eq:rcf}\eqref{eq:to_cf}
\item Extract the Plant's characteristic polynomial coefficients from $P_a$. %the last row of $P_a=(\mat{T}\mat{A}\mat{T}^-1)_{n*}$.
\item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors: %($\frac{q_1}{2},\frac{q_2}{2},q_3$)
$$N=\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] 
\wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
\item Calculate a set of initial bounds on K based on the input constraints. Note that these bounds will be used during the 
synthesis phase to reduce the size of the solution space.
$$\phi_{safety} \Leftrightarrow u_k=-Kx_k : x_0 \in [\underline{x_0} \ \overline{x_0}] \wedge u_k \in [\underline{u}\ \ \overline{u}]$$
\item In this phase we synthesise a candidate controller
%We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a single iteration, in addition to a stability 
% specification defined by Jury's 
%criteria. %, and try to synthesise a controller that meets these specs.
% For a stabilized closed-loop, which is necessary for our safety property, we need
% these roots to remain within the unit circle, which we verify using Jury's criteria.
% Notice that in our polynomials $c_0=1$ and we only use reals.
% Once we have established convergence, we may examine the 
% safety specification $\phi_{safety}$.
as a model $\mat{K} \in \mathbb{R}\langle I,F\rangle^n$. We obtain it by solving the SAT formula 
$$\mathcal{J}_K=\mathcal{J}\langle I,F \rangle (P_{a-k},\mat{T})\wedge \phi_{safety}$$ 
that satisfies the input constraint and Jury's criteria for 
$P_{a-k}=z^n+\sum_{i=1}^n (a_i-k_i) z^{n-i} : k_i \in \mat{K} \wedge \tilde{\mat{K}}=\mat{K}\mat{T}$,
where $\mathcal{J}\langle I,F \rangle (P,\mat{T})$ is a program describing Jury's method.
If there is no candidate solution we return UNSAT and exit the loop.
\item Once we have a candidate solution, we perform a safety verification % If this step fails, we find a counterexample iteration and initial state and create a new constraint to refine our abstraction.
consisting of evaluating the progression of the system over time,
$x_{k+1} \models \phi_{safety}$. For this purpose we require 
an initial set $\phi_{init}= x_0 \in [\underline{x_0} \ \overline{x_0}]$ 
from which the system progresses. % Obviously, this set $x_0$ 
% must satisfy the specification; otherwise, the system will be unsafe to begin with.
% We accept a specification in the form $\mat{E}\mat{T}x_0<\mat{f}$. 
% The presence of $\mat{T}$ is because this will typically be given in the original 
% state-space.
Next, we use abstract acceleration to get a second abstraction that 
encompasses the accelerated continuous reach-tube over an unbounded time.
Accelerating \eqref{eq:observer_LTI_cf}, we obtain:
\begin{align}
%\label{eq:acc_observer_LTI_cf}
x=&\mat{A}_t^kx_0
%+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{t} r_i
+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{n}(\nu_1+\nu_2+\nu_3) : x_0 \models \phi_{init}
\end{align}
which would still require us to verify the system for every $k$ up to infinity. 
Instead we use abstract acceleration~\cite{cattaruzza2015unbounded}, which translates the formula into
\begin{align}
\label{eq:aa_observer_LTI_cf}
\hat{X}^\#
=&\mathcal{A}_t X_0+\mathcal{B}_{t} R + \mathcal{B}_{n} N\\
X_0 =&\left \{x : x \models \phi_{init} \right\}\nonumber\\
% R =&\{r : \mat{E}_r < f_r \}\nonumber\\
 %N=&\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] \wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber
\end{align}
where $\mathcal{A}_t=\bigcup_{k=1}^\infty \mat{A}^k, \mathcal{B}_{t}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{t}, \mathcal{B}_{n}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{n}$ are abstract matrices for the system in \eqref{eq:observer_LTI_cf} 
%and $r$ is a non-deterministic parametric input (\emph{ie} $\forall k>0, r_{k+1} =r_k$) 
whereas the set N is composed of non-deterministic variable inputs.
